Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-09 ms.tex
More conclusion.

    It is also possible that many of the galaxies in the
    \citet{Miller+15} are accreting in a non-steady fashion and this
    scatter arises from cyclic variation in accretion rate. In fact it
    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
    \Msun$ coexists with a population of smaller, steadily accreting
    black holes (e.g. the upper limits in \citet{Miller+15}).  This
    calls into question the use of simple extrapolations of power-law
    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
    to constrain the occupation fraction of black holes in low mass
    galaxies (\citealt{Miller+15}).
  \item Low mass AGN have growth times comparable to the Hubble time
    \citet{Heckman+04}. We have shown that this would require accretion
    rates not consistent with steady-state thermally stable accretion
    of stellar wind material, and is driven by an external supply of gas.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they agree to
    within a factor of order unity. This is because in our model the
    accretion rate is determined by the flow properties at the
    stagnation radius, $\rs$, which is within a factor of a few of the
    Bondi radius $\rb$. Thus, use of the Bondi formula is a
    good approximation.
  \end{enumerate}

>>>>

    It is also possible that many of the galaxies in the
    \citet{Miller+15} are accreting in a non-steady fashion and this
    scatter arises from cyclic variation in accretion rate. In fact it
    that a population of cyclically accreting with $\Mbh\gsim 10^{8}
    \Msun$ coexists with a population of smaller, steadily accreting
    black holes (e.g. the upper limits in \citet{Miller+15}).  This
    calls into question the use of simple extrapolations of power-law
    fits to the $L_{\rm X}(M_{\bullet}$) relationship to low $M_{\bullet}$
    to constrain the occupation fraction of black holes in low mass
    galaxies (\citealt{Miller+15}).
  \item Low mass AGN have growth times comparable to the Hubble time
    \citet{Heckman+04}. We have shown that this would require accretion
    rates not consistent with steady-state thermally stable accretion
    of stellar wind material, and is driven by an external supply of gas.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they agree to
    within a factor of order unity. This is because in our model the
    accretion rate is determined by the flow properties at the
    stagnation radius, $\rs$, which is within a factor of a few of the
    Bondi radius $\rb$. Thus, use of the Bondi formula is a
    good approximation.

    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
    the observed nuclear x-ray luminosities in quiescent, early type
    galaxies could be understood as coming from thermally stable
    steady-state accretion of stellar winds shed in the galactic
    nucleus.  However, we would like to draw attention to the
    following limitations of our model

    \begin{enumerate}
    \item Overall the accretion rate onto the cetral SMBH will be strongly
    tied to the properties of the stellar population (e.g. age) within
    the sphere of influence of the black hole. Thus, our model cannot
    say anything definitive about the mode accretion for indivudual
    galaxies which may have significant variations about our assumed
    average star formation histories.
    \item Also, the star formation history of bulges may (and probably
      does) systematically differ from the average star formation
      history for galaxies as a whole.
    \item Furthermore, there could be a radial gradient in the star
      formation history within a given bulge... 
    \end{enumerate}
